Networked Character Devices

### 2011-12-10 report/presentation.tex
Goal page & Overview page

\begin{frame}{\bf NCD Overview}
  \begin{itemize}
    \item<1-> Stuff
    \item<2-> Motivation: transparent remote device usage
    \item<3-> Client: kernel module (Linux 2.6.x+)
    \item<4-> Server: userspace daemon
    \item<5-> Current Project Status:
    \begin{itemize}
      \item<6-> successful implementation
      \item<6-> rough around the edges
      \item<6-> very clear focus for future work
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{\bf NCD Overview}
  \begin{itemize}
    \item<1-> Motivation: providing transparent access to remote devices opens up a new paradigm of storage and device usage
    \begin{itemize}
      \item<2-> Physical locality only needed for lower latency
    \end{itemize}
    \item<3-> Project attributes:
    \begin{itemize}
      \item<4-> Client: kernel module (Linux 2.6.x+)
      \item<5-> Server: userspace daemon
      \item<6-> Current Project Status:
        \begin{itemize}
          \item<7-> Successful implementation
          \item<8-> Rough around the edges
          \item<9-> More development required for certain devices
          \item<10-> Very clear focus for future work
        \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}
